\newcommand{\ackspace}{\vspace{0.3cm}}
\newcommand{\ackspacebullet}{}

The writing of this thesis marks the end of a large chapter in my life, a chapter filled with intense learning moments, interleaved with lighter, funnier times, as well as moments of deep reflection that enabled me to grow as a person.
As last words of this life chapter, I deeply wish to thank from the bottom of my hearth all the people around me that shaped and made possible these last years:\ackspacebullet
\begin{itemize}
	\itemsep 0em
	\item I wish to thank all the numerous professors that dedicated their time and effort to transmit a fraction of their extensive knowledge to me.
	      Thanks for all the passion that you dedicate every day to form the generations that will shape the future.\ackspacebullet
	\item I wish to thank professor Cantoro for being my thesis supervisor.
	      Despite the thesis not ending up in your research interest, your presence was still extremely valuable in directing the overall structure of this paper.
	      On top of that, the knowledge you passed me with your GPU Programming course has been extremely versatile while developing the different approaches described in this document.\ackspacebullet
	\item I wish to thank my family, mostly my parents Fulvio and Daniela and my sister Valentina, for your continuous support in both moral and economical term.
	      Thanks for the way you grew me up, thanks for always believing in me, for being there when I needed support.
	      Thanks for pushing me to go forward even when my decisions were not matching your expectations.\ackspacebullet
	\item I wish to thank my grandparents Franco, Luciana, Domenico and Secondina, and all my relatives in general.
	      You always trusted and encouraged me to be the best version of myself, teaching me with your example.\ackspacebullet
	\item I wish to thank Samuele, my travel companion in Turin for all these years.
	      Thanks for inviting me to rent a room in your apartment: that house and the memories I have in it will forever live in my hearth.
	      Thanks for all the train trips we had together, the meals and cooking times we shared, the games we played together.\ackspacebullet
	\item I wish to thank my university friends Davide, Federico and Giacomo.
	      The university years are not only a time to get filled of knowledge, but mostly they aim to expand one's relationships, interests and horizons.
	      With all your chatting, suggestions, quirky behaviors and ideas, you sculpted a great portion of how I am right now.\ackspacebullet
	\item I wish to thank Kamel and François for all the practical suggestions that you gave me during my stay at SMA-RTY.
	      Thanks for doing whatever was in your power to make me feel welcomed, not only in the office, but in Clermont in general.\ackspacebullet
	\item I wish to thank John and Yorick, not only you were office colleagues, you became real friends for me.
	      Thanks for all the lunches and coffee-breaks we had together, for all the discussions and shared knowledge.\ackspacebullet
	\item I wish to thank Edoardo for being my \textit{Italian of reference} in the office.
	      Thanks for the discussions about the problems I was encountering: talking with someone was always a good way to find new creative solutions.
	      Thanks also for the more relaxed moments: it was a relief to have someone to whom I was able to speak Italian, to relax my brain from all the English and French I constantly had to speak.\ackspacebullet
	\item I wish to thank Emmanuel and Emilie, Anne and Louis, Jérôme and Laurence, and all the people I met at the church in Aubière.
	      Thanks for the warm welcome to the parish, thanks for inviting me to countless \textit{``repas''} and for asking me to play the guitar at the Mass.
	      You really filled my French weekends with joy, and allowed me to realize how we are all brothers in Christ, regardless of where we come from.\ackspacebullet
	\item I wish to thank my friends from Manta: Marta, Martina, Martina, Nicolò, Samuele, Simone and Stefano.
	      While not being directly present in my university career, you played a crucial role in creating lovely moments with me during the weekends.
	      Thanks for the countless dinners, games and chats we had together.\ackspacebullet
	\item Finally, I wish to thank all the people that are not in this list.
	      I strongly believe that we are what we are thanks to the sum of all the single events that happened in our lives.
	      I think that every action, every person, every word we experienced contributed to sculpt what we are today.
	      As such, I deeply desire to thank everyone that I met on my path, may it be \textit{for the life, or just a day}, as an Italian song says: thanks for making me as I am now, which I am really proud of.\ackspacebullet
\end{itemize}
As the people close to me probably already know, computer engineering was a deep passion of mine, but not the dream of my life.
After closing this chapter, I will soon open a new one, crowning the dream I had since I was a child.
I will be in Bremen, studying to become an airline pilot at the Lufthansa group flight school.\ackspace

I am certain that all the experiences lived this past chapter of my life will be of great support in this new adventure: once more, I deeply wish to thank everyone that contributed to it.
Finally, I would like to ask you a favor: as much as you supported me in this past few years, please continue to do so in the upcoming adventure.
It won't be easy, it won't be possible with the same modalities... but I really need your support.\ackspace

Thanks to everyone, \\
\null\hfill Francesco
